\chapter{Results}

\section{Overview}
\begin{itemize}
    \item Structure of results presentation: simulation results, physical testing results, and comparative analysis.
    \item Brief reminder of objectives and evaluation metrics from Chapter~\ref{chap:Methodology}.
\end{itemize}

\section{Simulation Results}
\begin{itemize}
    \item Accuracy of GPR model at different numbers of test points.
    \item BO performance in identifying nonlinear features (e.g., backbone curve, bifurcation points).
    \item Visualisations:
    \begin{itemize}
        \item FRF plots for selected amplitudes/frequencies.
        \item Response surface predictions with uncertainty bands.
        \item Acquisition function maps showing selected test points.
    \end{itemize}
    \item Quantitative comparison with uniform sampling:
    \begin{itemize}
        \item Prediction error metrics.
        \item Number of test points saved.
        \item Computational time comparisons.
    \end{itemize}
\end{itemize}

\section{Physical Testing Results}
\begin{itemize}
    \item Experimental FRFs from simplified beam-spring setup.
    \item Examples of observed nonlinear phenomena (e.g., amplitude-dependent frequency shift, jump phenomena).
    \item GPR model performance on experimental data.
    \item BO-driven test point selection in practice.
    \item Visualisations:
    \begin{itemize}
        \item Experimental vs predicted FRFs.
        \item Selected test points overlaid on measured data.
        \item Uncertainty reduction plots over iterations.
    \end{itemize}
\end{itemize}

\section{Comparison Between Simulation and Experiment}
\begin{itemize}
    \item Agreement in identified nonlinear features.
    \item Differences attributed to experimental noise, simplifications in the beam model, or measurement limitations.
    \item Discussion on the method’s robustness across simulation and real-world conditions.
\end{itemize}

\section{Summary of Findings}
\begin{itemize}
    \item Key quantitative and qualitative results.
    \item Observed advantages and limitations of BO + GPR in control-based testing.
    \item Lead-in to discussion and interpretation in Chapter~\ref{chap:Discussion}.
\end{itemize}
