\chapter{Conclusion and Future Work}

\section{Summary of Research}
\begin{itemize}
    \item Recap of project aims and objectives (as stated in Chapter~\ref{chap:Introduction}).
    \item Summary of the two-stage methodology:
    \begin{itemize}
        \item Numerical simulation of a nonlinear beam model using BO + GPR.
        \item Physical testing on a simplified beam-spring setup.
    \end{itemize}
    \item Rationale for combining control-based testing with data-driven modelling.
\end{itemize}

\section{Key Findings}
\begin{itemize}
    \item BO + GPR methodology reduced the number of test points compared to uniform sampling.
    \item Accurate prediction of nonlinear features (e.g., backbone curve, bifurcation points) in both simulation and experiment.
    \item Demonstrated applicability of method to noisy experimental data.
    \item Limitations observed when transitioning from simulation to physical testing.
\end{itemize}

\section{Contributions}
\begin{itemize}
    \item First application of BO + GPR in a control-based testing framework for nonlinear structural dynamics.
    \item Development of a simplified yet representative experimental setup for method validation.
    \item Evidence supporting the method’s potential for aerospace component testing.
\end{itemize}

\section{Limitations}
\begin{itemize}
    \item Simplified experimental setup does not fully replicate rotor blade dynamics.
    \item BO performance sensitive to initial sampling strategy.
    \item Control-based testing implementation challenges in high-noise environments.
\end{itemize}

\section{Future Work}
\begin{itemize}
    \item Application to full-scale rotor blade tests.
    \item Integration with advanced control strategies to stabilise unstable states.
    \item Exploration of alternative surrogate models and acquisition functions.
    \item Extension to multi-degree-of-freedom and coupled systems.
\end{itemize}

\section{Closing Remarks}
\begin{itemize}
    \item Reflection on the project’s significance in advancing efficient nonlinear dynamic testing.
    \item Potential industrial impact for aerospace structural characterisation.
\end{itemize}
